---
output:
  html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>
<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>
<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>
<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>
<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>
<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->
<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->
```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}

# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
  library(lubridate)
})

# devtools::install_github("hafen/lazyrmd")
# require(lazyrmd)
# 
# options(repos = c(tessera = "http://packages.tessera.io",
#   getOption("repos")))
# install.packages("lazyrmd")
# require(lazyrmd)

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================

# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )

# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors

MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}

# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 

  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color

# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)

# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order

MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}



# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}

# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}

# Use in ggplot 
  # scale_color_MountSinai("main")

```


```{r Global Functions, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y)) # Does not include
not_all_na <- function(x) all(!is.na(x)) # Exclude columns with All NAs

```


```{r Data Connections, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)
conn3 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB Production", timeout = 30)
conn2 <- dbConnect(odbc(), 
                  "Clarity_prod", 
                  uid = "kweons01" , 
                  pwd = "kweons01123$")
conn4 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB Staging", timeout = 30)

conn5 <- dbConnect(odbc(),
                    Driver = "SQLServer",
                    # Server = "10.2.42.69", # old server
                    Server = "datahub-synapse.sql.azuresynapse.net",
                    database = "datahub_epic_dw",
                    UID = "MSS_USER",
                    PWD = "Apple_Bees456$",
                    Port = 1433)



# Clarity Connection  ------------------------------------------------
slot_raw_tbl <- tbl(conn2, "Y_DM_BOOKED_FILLED_RATE")
access_raw_tbl <- tbl(conn2, "MV_DM_PATIENT_ACCESS")
f_sched_appt_tbl <- tbl(conn2, "F_SCHED_APPT")
availability_raw_tbl <- tbl(conn2, "V_AVAILABILITY")
block_raw_tbl <- tbl(conn2, "AVAIL_BLOCK")
block_name_tbl <- tbl(conn2, "ZC_APPT_BLOCK")
orders_raw_tbl <- tbl(conn2, "ORDER_PROC")
visit_type_tbl <- tbl(conn2, "CL_PRC_VT_GROUPS")
visit_type_mapping_tbl <- tbl(conn2, "ZC_VISIT_TYPE_GRP")

dep_mapping_tbl <- tbl(conn2, "CLARITY_DEP")
dep_mapping <- dep_mapping_tbl %>%
  # dplyr::select(DEPARTMENT_ID, SPECIALTY) %>%
  collect()

clarity_ser_tbl <- tbl(conn2, "CLARITY_SER")
clarity_ser_2_tbl <- tbl(conn2, "CLARITY_SER_2")

finclass_tbl <- tbl(conn2, "V_PB_EPP_CUSTOM_PRD_TYPE")


# Local Connection ---------------------------------------------------
radiology_dep_mapping_tbl <- tbl(conn1, "RADIOLOGY_DEP_MAPPING")

clarity_ser_tbl_loc <- tbl(conn1, "CLARITY_SER")
clarity_ser_2_tbl_loc <- tbl(conn1, "CLARITY_SER_2")

dep_mapping_tbl_loc <- tbl(conn1, "CLARITY_DEP")

slot_data_raw_tbl <- tbl(conn1, "ALL_SLOTS")
slot_data_tbl <- tbl(conn1, "SLOT_DATA")
slot_data_prc_raw_tbl <- tbl(conn1, "ALL_SLOTS_PRC")
slot_data_prc_tbl <- tbl(conn1, "SLOT_DATA_PRC")

block_raw_tbl_loc <- tbl(conn1, "AVAIL_BLOCK")
block_name_tbl_loc <- tbl(conn1, "ZC_APPT_BLOCK")




#slot_view_tbl <- tbl(conn3, in_schema("OAO_PRODUCTION", "AMBULATORY_SLOT_TABLE"))


# Azure Connection ---------------------------------------------------
# access_raw_tbl <- tbl(conn5, in_schema("CLARITY", "MV_DM_PATIENT_ACCESS"))
# f_sched_appt_tbl <- tbl(conn5, dbplyr::ident_q('"CLARITY"."F_SCHED_APPT"'))
clarity_dep_conn <- tbl(conn5, dbplyr::ident_q('"Clarity"."CLARITY_DEP"'))

referrals_conn <- tbl(conn5, dbplyr::ident_q('"MS_SOLUTIONS_DEV"."y_s2_referrals_tmp"'))
caboodle_referrals_conn <- tbl(conn5, dbplyr::ident_q('"CABOODLE"."ReferralsDataView"'))
caboodle_referralFact_conn <- tbl(conn5, dbplyr::ident_q('"CABOODLE"."ReferralFact"'))
patient_conn <- tbl(conn5, dbplyr::ident_q('"CABOODLE"."PatientDim"'))
department_conn <- tbl(conn5, dbplyr::ident_q('"CABOODLE"."DepartmentDim"'))

clarity_referrals_tbl <- tbl(conn5, dbplyr::ident_q('"Clarity"."REFERRAL"'))
clarity_referrals_wq_tbl <- tbl(conn5, dbplyr::ident_q('"Clarity"."REFERRAL_WQ"'))

visitFact_conn <- tbl(conn5, dbplyr::ident_q('"Caboodle"."VisitFact"'))


```


```{r Report Variables, echo = FALSE, warning = FALSE, message = FALSE}

report_run_date <- Sys.Date()
date_start <- format(Sys.Date(), "%Y-%m-%d")
date_next_14days <- format(Sys.Date() +14, "%Y-%m-%d")
slot_date_start <- format(Sys.Date() -1, "%Y-%m-%d")
# date_start <- paste0(format(Sys.Date(), "%Y-%m"),"-01")

current_year <- format(report_run_date, "%Y")
prior_year <- as.character(as.numeric(current_year) -1)
baseline_year <- as.character(as.numeric(current_year) -2)

current_month <- format(report_run_date, "%m")

current_year_month <- paste0(current_year,"-",current_month)
```


```{r Mount Sinai Holidays}


holidays <- data.frame(
  holiday = c("New Year's Day",
              "MLK Day",
              "President's Day",
              "Memorial Day",
              "Juneteenth",
              "Independence Day",
              "Labor Day",
              "Thanksgiving Day",
              "Christmas Day",
              "New Year's Day",
              "MLK Day",
              "President's Day",
              "Memorial Day",
              "Juneteenth",
              "Independence Day",
              "Labor Day",
              "Thanksgiving Day",
              "Christmas Day"
              ),
  date = c("1/1/2025",
                 "1/20/2025",
                "2/17/2025",
                "5/26/2025",
                "6/19/2025",
                "7/4/2025",
                "9/1/2025",
                "11/27/2025",
                "12/25/2025",
                "1/1/2026",
                "1/19/2026",
                "2/16/2026",
                "5/26/2026",
                "6/19/2026",
                "7/3/2026",
                "9/7/2026",
                "11/26/2026",
                "12/25/2026"
                )
  )

holidays <- holidays %>%
  mutate(week_start = floor_date(as.Date(date, "%m/%d/%Y"), unit = "week", week_start = 1))

```


```{r Friday Volume Opportunity Analysis by Week}

date_start <- as.Date("2025-12-29")
date_end <- as.Date(Sys.Date() - 1)
date_end <- date_end - as.integer(format(date_end, "%u"))


## Scheduled Volume Comparison -------------------------------------------------

scheduled_volume <- access_raw_tbl %>%
  left_join(clarity_ser_tbl %>% select(PROV_ID, PROV_TYPE)) %>%
  # filter(PROV_TYPE == "Physician") %>%
  left_join(clarity_ser_2_tbl %>% dplyr::select(PROV_ID, NPI)) %>%
  # filter(!is.na(SITE)) %>%
  # filter(SITE %in% c("MSUS", "MSH- AMBULATORY CARE", "NETWORK", "MSW", "MSH-MSDFP",
  #                    "MSDMG", "MSB", "MSM", "MSQ", "MSBI", "MSSN", "NYEE")) %>%
  mutate(lead_days = CONTACT_DATE - APPT_MADE_DATE) %>%
  mutate(cancel_lead_days = APPT_DTTM - APPT_CANC_DTTM) %>%
  # mutate(lead_days =  as.numeric(difftime(as.Date(APPT_MADE_DATE), as.Date(CONTACT_DATE), units = "days"))) %>%
  # mutate(SPECIALTY_GRP = ifelse(DEPT_SPECIALTY_NAME %in%
  #                                 c("Adolescent Medicine", "Community and Preventive Medicine",
  #                                   "Family Medicine", "Internal Medicine", "Pediatrics", "Geriatrics", "Gerontology", "Urgent Care"), "Primary Care", "Specialty")) %>%
  filter((CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS") & 
                                    CONTACT_DATE <= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & 
             (DERIVED_STATUS_DESC == "Arrived" |
                DERIVED_STATUS_DESC == "No Show" |
                (DERIVED_STATUS_DESC == "Canceled"  & cancel_lead_days <= 1) |
                (DERIVED_STATUS_DESC == "Rescheduled" & cancel_lead_days <= 1))) |
           (DERIVED_STATUS_DESC == "Scheduled" & (CONTACT_DATE >= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & year(CONTACT_DATE) <= 2026))) %>%
  mutate(DERIVED_STATUS_DESC = "Scheduled") %>%
  mutate(appt_year = year(CONTACT_DATE),
         appt_month = month(CONTACT_DATE),
         appt_week = sql("TRUNC(CONTACT_DATE, 'IW')"),
         appt_day = sql("TRIM(TO_CHAR(CONTACT_DATE, 'DAY'))")) %>%
  mutate(appt_made_year = year(APPT_MADE_DATE),
         appt_made_month = month(APPT_MADE_DATE)) %>%
  mutate(visit_type = ifelse(is.na(VISIT_GROUP_NUM), "ESTABLISHED", "NEW")) %>%
  mutate(lead_14days = ifelse(lead_days <= 14, "lead_14days", "lead_14days_more")) %>%
  # filter(CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  # filter(CONTACT_DATE <= TO_DATE(date_end , "YYYY-MM-DD HH24:MI:SS")) %>%
  # dplyr::select(SITE, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, DEPARTMENT_ID, PROV_NAME_WID, PAT_ENC_CSN_ID, APPT_STATUS_NAME, CANCEL_LEAD_HOURS, CANCEL_INITIATOR) %>%
  group_by(SITE, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, DEPARTMENT_ID, PROV_ID, NPI, PROV_NAME_WID, PROV_TYPE,
           appt_week, appt_day,
           # appt_day, CONTACT_DATE,
           DERIVED_STATUS_DESC) %>%
    # group_by(
    #        appt_week, appt_day,
    #        # appt_day, CONTACT_DATE,
    #        DERIVED_STATUS_DESC) %>%
  summarise(total = n()) %>%
  collect() %>%
  pivot_wider(names_from = c("DERIVED_STATUS_DESC", "appt_day"),
              values_from = total,
              values_fill = 0)

scheduled_volume <- scheduled_volume %>%
  mutate(Scheduled_AVG = sum(Scheduled_MONDAY, Scheduled_TUESDAY, Scheduled_WEDNESDAY, Scheduled_THURSDAY)/4) %>%
  mutate(Scheduled_VAR = Scheduled_FRIDAY - Scheduled_AVG,
         Scheduled_VAR_PERC = Scheduled_VAR/Scheduled_AVG)


## Arrived Volume and No Show Rate Comparison ----------------------------------

volume_no_show <- access_raw_tbl %>%
  left_join(clarity_ser_tbl %>% select(PROV_ID, PROV_TYPE)) %>%
  # filter(PROV_TYPE == "Physician") %>%
  left_join(clarity_ser_2_tbl %>% dplyr::select(PROV_ID, NPI)) %>%
  # filter(!is.na(SITE)) %>%
  # filter(SITE %in% c("MSUS", "MSH- AMBULATORY CARE", "NETWORK", "MSW", "MSH-MSDFP",
  #                    "MSDMG", "MSB", "MSM", "MSQ", "MSBI", "MSSN", "NYEE")) %>%
  mutate(lead_days = CONTACT_DATE - APPT_MADE_DATE) %>%
  mutate(cancel_lead_days = APPT_DTTM - APPT_CANC_DTTM) %>%
  # mutate(lead_days =  as.numeric(difftime(as.Date(APPT_MADE_DATE), as.Date(CONTACT_DATE), units = "days"))) %>%
  # mutate(SPECIALTY_GRP = ifelse(DEPT_SPECIALTY_NAME %in%
  #                                 c("Adolescent Medicine", "Community and Preventive Medicine",
  #                                   "Family Medicine", "Internal Medicine", "Pediatrics", "Geriatrics", "Gerontology", "Urgent Care"), "Primary Care", "Specialty")) %>%
  filter(DERIVED_STATUS_DESC == "Arrived" |
           DERIVED_STATUS_DESC == "No Show" |
           (DERIVED_STATUS_DESC == "Canceled"  & cancel_lead_days <= 1) |
           (DERIVED_STATUS_DESC == "Rescheduled" & cancel_lead_days <= 1)) %>%
  mutate(DERIVED_STATUS_DESC = ifelse(DERIVED_STATUS_DESC == "No Show", "No_Show", DERIVED_STATUS_DESC)) %>%
  mutate(appt_year = year(CONTACT_DATE),
         appt_month = month(CONTACT_DATE),
         appt_week = sql("TRUNC(CONTACT_DATE, 'IW')"),
         appt_day = sql("TRIM(TO_CHAR(CONTACT_DATE, 'DAY'))")) %>%
  mutate(appt_made_year = year(APPT_MADE_DATE),
         appt_made_month = month(APPT_MADE_DATE)) %>%
  mutate(visit_type = ifelse(is.na(VISIT_GROUP_NUM), "ESTABLISHED", "NEW")) %>%
  mutate(lead_14days = ifelse(lead_days <= 14, "lead_14days", "lead_14days_more")) %>%
  filter(CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  filter(CONTACT_DATE <= TO_DATE(report_run_date , "YYYY-MM-DD HH24:MI:SS")) %>%
  # dplyr::select(SITE, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, DEPARTMENT_ID, PROV_NAME_WID, PAT_ENC_CSN_ID, APPT_STATUS_NAME, CANCEL_LEAD_HOURS, CANCEL_INITIATOR) %>%
  group_by(SITE, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, DEPARTMENT_ID, PROV_ID, NPI, PROV_NAME_WID, PROV_TYPE, 
           appt_week, appt_day,
           # appt_day, CONTACT_DATE,
           DERIVED_STATUS_DESC) %>%
  summarise(total = n()) %>%
  collect() %>%
  pivot_wider(names_from = c("DERIVED_STATUS_DESC", "appt_day"),
              values_from = total,
              values_fill = 0)


volume_no_show <- volume_no_show %>%
  mutate(Arrived_AVG = sum(Arrived_MONDAY, Arrived_TUESDAY, Arrived_WEDNESDAY, Arrived_THURSDAY)/4) %>%
  mutate(Arrived_VAR = Arrived_FRIDAY - Arrived_AVG,
         Arrived_VAR_PERC = Arrived_VAR/Arrived_AVG) %>%
  mutate(No_Show_AVG = sum(No_Show_MONDAY, No_Show_TUESDAY, No_Show_WEDNESDAY, No_Show_THURSDAY)/4,
         Canceled_AVG = sum(Canceled_MONDAY, Canceled_TUESDAY, Canceled_WEDNESDAY, Canceled_THURSDAY)/4,
         Rescheduled_AVG = sum(Rescheduled_MONDAY, Rescheduled_TUESDAY, Rescheduled_WEDNESDAY, Rescheduled_THURSDAY)/4) %>%
  mutate(No_Show_Rate_AVG = (No_Show_AVG + Canceled_AVG + Rescheduled_AVG) / (No_Show_AVG + Canceled_AVG + Rescheduled_AVG + Arrived_AVG),
         No_Show_Rate_FRIDAY = (No_Show_FRIDAY + Canceled_FRIDAY + Rescheduled_FRIDAY) / (No_Show_FRIDAY + Canceled_FRIDAY + Rescheduled_FRIDAY + Arrived_FRIDAY))



## Session Count ---------------------------------------------------------------
sessions <- access_raw_tbl %>%
  filter(CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  filter(CONTACT_DATE <= TO_DATE(date_end , "YYYY-MM-DD HH24:MI:SS")) %>%
  mutate(cancel_lead_days = APPT_DTTM - APPT_CANC_DTTM) %>%
  filter((CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS") & 
                                    CONTACT_DATE <= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & 
             (DERIVED_STATUS_DESC == "Arrived" |
                DERIVED_STATUS_DESC == "No Show" |
                (DERIVED_STATUS_DESC == "Canceled"  & cancel_lead_days <= 1) |
                (DERIVED_STATUS_DESC == "Rescheduled" & cancel_lead_days <= 1))) |
           (DERIVED_STATUS_DESC == "Scheduled" & (CONTACT_DATE >= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & year(CONTACT_DATE) <= 2026))) %>%
  mutate(appt_year = year(CONTACT_DATE),
         appt_month = month(CONTACT_DATE),
         appt_week = sql("TRUNC(CONTACT_DATE, 'IW')"),
         appt_day = sql("TRIM(TO_CHAR(CONTACT_DATE, 'DAY'))")) %>%
  group_by(DEPARTMENT_ID, PROV_ID, appt_week, appt_day, CONTACT_DATE) %>%
  summarise(
    first_appt = min(APPT_DTTM),
    last_appt  = max(APPT_DTTM),
    first_last_appt_hour = (max(APPT_DTTM) - min(APPT_DTTM)) * 24,
    .groups = "drop"
  ) %>%
  mutate(total = ifelse(first_last_appt_hour<2,0, ifelse(first_last_appt_hour<5,1, ifelse(first_last_appt_hour<9,2,3)))) %>%
  group_by(DEPARTMENT_ID, PROV_ID, appt_week, appt_day) %>%
  summarise(total = sum(total, na.rm = T)) %>%
  collect() %>%
  mutate(session_cnt = "session_cnt") %>%
  pivot_wider(names_from = c("session_cnt", "appt_day"),
              values_from = total,
              values_fill = 0) %>%
  mutate(session_cnt_AVG = sum(session_cnt_MONDAY + session_cnt_TUESDAY + session_cnt_WEDNESDAY + session_cnt_THURSDAY)/4) %>%
  mutate(session_cnt_VAR = session_cnt_FRIDAY - session_cnt_AVG,
         session_cnt_VAR_PERC = session_cnt_VAR/session_cnt_AVG)

  

## Physician Count ---------------------------------------------------------------
physicians <- access_raw_tbl %>%
  filter(CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  filter(CONTACT_DATE <= TO_DATE(date_end , "YYYY-MM-DD HH24:MI:SS")) %>%
  mutate(cancel_lead_days = APPT_DTTM - APPT_CANC_DTTM) %>%
  filter((CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS") & 
                                    CONTACT_DATE <= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & 
             (DERIVED_STATUS_DESC == "Arrived" |
                DERIVED_STATUS_DESC == "No Show" |
                (DERIVED_STATUS_DESC == "Canceled"  & cancel_lead_days <= 1) |
                (DERIVED_STATUS_DESC == "Rescheduled" & cancel_lead_days <= 1))) |
           (DERIVED_STATUS_DESC == "Scheduled" & (CONTACT_DATE >= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & year(CONTACT_DATE) <= 2026))) %>%
  mutate(appt_year = year(CONTACT_DATE),
         appt_month = month(CONTACT_DATE),
         appt_week = sql("TRUNC(CONTACT_DATE, 'IW')"),
         appt_day = sql("TRIM(TO_CHAR(CONTACT_DATE, 'DAY'))")) %>%
  group_by(DEPARTMENT_ID, PROV_ID, appt_week, appt_day) %>%
  summarise(total = n_distinct(PROV_ID)) %>%
  collect() %>%
  mutate(md_cnt = "md_cnt") %>%
  pivot_wider(names_from = c("md_cnt", "appt_day"),
              values_from = total,
              values_fill = 0) %>%
  mutate(md_cnt_AVG = sum(md_cnt_MONDAY + md_cnt_TUESDAY + md_cnt_WEDNESDAY + md_cnt_THURSDAY)/4) %>%
  mutate(md_cnt_VAR = md_cnt_FRIDAY - md_cnt_AVG,
         md_cnt_VAR_PERC = md_cnt_VAR/md_cnt_AVG)
  

# Unfilled Slots ---------------------------------------------------------------
grp_mapping <- data.frame("SITE" = c("NETWORK", "OTHER", "MSH-MSDFP", "MSUS", 
                                        "MSDMG", "MSBI", "MSW", "MSHP", "MSM", "MSH- AMBULATORY CARE",
                                        "NYEE", "MS NOW", "MSQ", "MSSN", "MSB"),
                             "RPT_GRP_SEVNTEEN_C" = c(2, 3,4, 6, 
                                                      7, 8, 9, 10, 11, 12,
                                                      13, 14, 15, 19, 38))


unfilled_slots <- tbl(conn2, "V_AVAILABILITY") %>%
  # filter(DEPARTMENT_ID == 8001059) %>%
  # filter(PROV_ID == 377151) %>%
  # filter(year(SLOT_BEGIN_TIME) ==  2026) %>%
  # filter(month(SLOT_BEGIN_TIME) == 1) %>%
  # left_join(clarity_ser_2_tbl %>% dplyr::select(PROV_ID, NPI)) %>%
  filter(SLOT_BEGIN_TIME >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  filter(year(SLOT_BEGIN_TIME) <= 2026) %>%
  mutate(slot_date = sql("TRUNC(SLOT_BEGIN_TIME)"),
         slot_year = year(SLOT_BEGIN_TIME),
         slot_month = month(SLOT_BEGIN_TIME),
         slot_day = sql("TO_CHAR(TRUNC(SLOT_BEGIN_TIME), 'FMDAY')"),
         slot_week = sql("TRUNC(SLOT_BEGIN_TIME, 'IW')")) %>%
  filter(TIME_HELD_YN == "N" | TIME_UNAVAIL_YN == "N") %>%
  filter(SLOT_LENGTH >= 10) %>%
  filter(as.numeric(SLOT_HOUR) >= 7 & as.numeric(SLOT_HOUR) <= 21) %>%

  # Exclude any dates with 0 appts scheduled (false template)
  group_by(DEPARTMENT_ID, PROV_ID, slot_date) %>%
  mutate(apts_scheduled = sum(NUM_APTS_SCHEDULED, na.rm = T)) %>%
  filter(apts_scheduled > 0) %>%
  filter(APPT_NUMBER == 0) %>%
  filter(ORG_REG_OPENINGS - NUM_APTS_SCHEDULED > 0) %>%

  group_by(DEPARTMENT_ID, PROV_ID, slot_week, slot_day) %>%
  summarise(total = n()) %>%
  collect() %>%
  mutate(unfilled_cnt = "unfilled_cnt") %>%
  pivot_wider(names_from = c("unfilled_cnt", "slot_day"),
              values_from = total,
              values_fill = 0) %>%
  mutate(unfilled_cnt_AVG = sum(unfilled_cnt_MONDAY + unfilled_cnt_TUESDAY + unfilled_cnt_WEDNESDAY + unfilled_cnt_THURSDAY)/4) %>%
  mutate(unfilled_cnt_VAR = unfilled_cnt_FRIDAY - unfilled_cnt_AVG,
         unfilled_cnt_VAR_PERC = unfilled_cnt_VAR/unfilled_cnt_AVG)
  

  
  
## Merged Data -----------------------------------------------------------------
merged_data <- full_join(scheduled_volume, volume_no_show)
merged_data <- full_join(merged_data, sessions)
merged_data <- full_join(merged_data, physicians)
merged_data <- left_join(merged_data, unfilled_slots,
                         by = c("DEPARTMENT_ID" = "DEPARTMENT_ID",
                                "PROV_ID" = "PROV_ID",
                                "appt_week" = "slot_week"))


location <- tbl(conn1, "EPIC_DEPT_LOCATION_MAPPING") %>% collect()

merged_data <- merged_data %>%
  left_join(location %>% dplyr::select(DEPARTMENT_ID, STANDARD_ADDRESS)) %>%
  left_join(holidays %>% dplyr::select(holiday, week_start), 
            by = c("appt_week" = "week_start")) %>%
  mutate(appt_week = as.character(appt_week)) %>%
  arrange(appt_week, STANDARD_ADDRESS, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, PROV_TYPE, PROV_NAME_WID)

# require(openxlsx)
# write.xlsx(friday_data, "Friday Volume_040926.xlsx")


col_order <- c("appt_week", "holiday",
               "SITE", "STANDARD_ADDRESS",  "DEPT_SPECIALTY_NAME", "DEPARTMENT_NAME", "DEPARTMENT_ID", "PROV_TYPE", "PROV_ID", "NPI", "PROV_NAME_WID",
               "Scheduled_AVG", "Scheduled_MONDAY", "Scheduled_TUESDAY", "Scheduled_WEDNESDAY", "Scheduled_THURSDAY", "Scheduled_FRIDAY", "Scheduled_SATURDAY", "Scheduled_SUNDAY",
               "Scheduled_VAR", "Scheduled_VAR_PERC",
               "Arrived_AVG", "Arrived_MONDAY", "Arrived_TUESDAY", "Arrived_WEDNESDAY", "Arrived_THURSDAY", "Arrived_FRIDAY", "Arrived_SATURDAY", "Arrived_SUNDAY",
               "Arrived_VAR", "Arrived_VAR_PERC",
               "md_cnt_AVG", "md_cnt_MONDAY", "md_cnt_TUESDAY", "md_cnt_WEDNESDAY", "md_cnt_THURSDAY", "md_cnt_FRIDAY", "md_cnt_SATURDAY", "md_cnt_SUNDAY",
               "md_cnt_VAR", "md_cnt_VAR_PERC",
               "session_cnt_AVG", "session_cnt_MONDAY", "session_cnt_TUESDAY", "session_cnt_WEDNESDAY", "session_cnt_THURSDAY", 
               "session_cnt_FRIDAY", "session_cnt_SATURDAY", "session_cnt_SUNDAY",
               "session_cnt_VAR", "session_cnt_VAR_PERC",
               "unfilled_cnt_AVG", "unfilled_cnt_MONDAY", "unfilled_cnt_TUESDAY", "unfilled_cnt_WEDNESDAY", "unfilled_cnt_THURSDAY", 
               "unfilled_cnt_FRIDAY", "unfilled_cnt_SATURDAY", "unfilled_cnt_SUNDAY",
               "unfilled_cnt_VAR", "unfilled_cnt_VAR_PERC",
               "Canceled_AVG", "Canceled_MONDAY", "Canceled_TUESDAY", "Canceled_WEDNESDAY", "Canceled_THURSDAY", "Canceled_FRIDAY", "Canceled_SATURDAY", "Canceled_SUNDAY",
               "Rescheduled_AVG", "Rescheduled_MONDAY", "Rescheduled_TUESDAY", "Rescheduled_WEDNESDAY", "Rescheduled_THURSDAY",
               "Rescheduled_FRIDAY", "Rescheduled_SATURDAY", "Rescheduled_SUNDAY",
               "No_Show_AVG", "No_Show_MONDAY", "No_Show_TUESDAY", "No_Show_WEDNESDAY", "No_Show_THURSDAY", "No_Show_FRIDAY", "No_Show_SATURDAY", "No_Show_SUNDAY",
               "No_Show_Rate_AVG", "No_Show_Rate_FRIDAY")


# setdiff(col_order, colnames(merged_data))


merged_data <- merged_data %>%
  dplyr::select(col_order)


```



```{r Friday Volume Opportunity Analysis by Month}

date_start <- as.Date("2026-1-1")
date_end <- as.Date(Sys.Date() - 1)
date_end <- date_end - as.integer(format(date_end, "%u"))



## Scheduled Volume Comparison -------------------------------------------------

scheduled_volume_month <- access_raw_tbl %>%
  left_join(clarity_ser_tbl %>% select(PROV_ID, PROV_TYPE)) %>%
  # filter(PROV_TYPE == "Physician") %>%
  left_join(clarity_ser_2_tbl %>% dplyr::select(PROV_ID, NPI)) %>%
  # filter(!is.na(SITE)) %>%
  # filter(SITE %in% c("MSUS", "MSH- AMBULATORY CARE", "NETWORK", "MSW", "MSH-MSDFP",
  #                    "MSDMG", "MSB", "MSM", "MSQ", "MSBI", "MSSN", "NYEE")) %>%
  mutate(lead_days = CONTACT_DATE - APPT_MADE_DATE) %>%
  mutate(cancel_lead_days = APPT_DTTM - APPT_CANC_DTTM) %>%
  # mutate(lead_days =  as.numeric(difftime(as.Date(APPT_MADE_DATE), as.Date(CONTACT_DATE), units = "days"))) %>%
  # mutate(SPECIALTY_GRP = ifelse(DEPT_SPECIALTY_NAME %in%
  #                                 c("Adolescent Medicine", "Community and Preventive Medicine",
  #                                   "Family Medicine", "Internal Medicine", "Pediatrics", "Geriatrics", "Gerontology", "Urgent Care"), "Primary Care", "Specialty")) %>%
  filter((CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS") & 
                                    CONTACT_DATE <= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & 
             (DERIVED_STATUS_DESC == "Arrived" |
                DERIVED_STATUS_DESC == "No Show" |
                (DERIVED_STATUS_DESC == "Canceled"  & cancel_lead_days <= 1) |
                (DERIVED_STATUS_DESC == "Rescheduled" & cancel_lead_days <= 1))) |
           (DERIVED_STATUS_DESC == "Scheduled" & (CONTACT_DATE >= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & year(CONTACT_DATE) <= 2026))) %>%
  mutate(DERIVED_STATUS_DESC = "Scheduled") %>%
  mutate(appt_year = year(CONTACT_DATE),
         appt_month = month(CONTACT_DATE),
         appt_week = sql("TRUNC(CONTACT_DATE, 'IW')"),
         appt_day = sql("TRIM(TO_CHAR(CONTACT_DATE, 'DAY'))")) %>%
  mutate(appt_made_year = year(APPT_MADE_DATE),
         appt_made_month = month(APPT_MADE_DATE)) %>%
  mutate(visit_type = ifelse(is.na(VISIT_GROUP_NUM), "ESTABLISHED", "NEW")) %>%
  mutate(lead_14days = ifelse(lead_days <= 14, "lead_14days", "lead_14days_more")) %>%
  # filter(CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  # filter(CONTACT_DATE <= TO_DATE(date_end , "YYYY-MM-DD HH24:MI:SS")) %>%
  # dplyr::select(SITE, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, DEPARTMENT_ID, PROV_NAME_WID, PAT_ENC_CSN_ID, APPT_STATUS_NAME, CANCEL_LEAD_HOURS, CANCEL_INITIATOR) %>%
  group_by(SITE, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, DEPARTMENT_ID, PROV_ID, NPI, PROV_NAME_WID, PROV_TYPE, 
           appt_year, appt_month, appt_day,
           # appt_day, CONTACT_DATE,
           DERIVED_STATUS_DESC) %>%
  summarise(total = n()) %>%
  collect() %>%
  pivot_wider(names_from = c("DERIVED_STATUS_DESC", "appt_day"),
              values_from = total,
              values_fill = 0)


scheduled_volume_month <- scheduled_volume_month %>%
  mutate(Scheduled_AVG = sum(Scheduled_MONDAY, Scheduled_TUESDAY, Scheduled_WEDNESDAY, Scheduled_THURSDAY)/4) %>%
  mutate(Scheduled_VAR = Scheduled_FRIDAY - Scheduled_AVG,
         Scheduled_VAR_PERC = Scheduled_VAR/Scheduled_AVG)


## Arrived Volume and No Show Rate Comparison ----------------------------------

volume_no_show_month <- access_raw_tbl %>%
  left_join(clarity_ser_tbl %>% select(PROV_ID, PROV_TYPE)) %>%
  # filter(PROV_TYPE == "Physician") %>%
  left_join(clarity_ser_2_tbl %>% dplyr::select(PROV_ID, NPI)) %>%
  # filter(!is.na(SITE)) %>%
  # filter(SITE %in% c("MSUS", "MSH- AMBULATORY CARE", "NETWORK", "MSW", "MSH-MSDFP",
  #                    "MSDMG", "MSB", "MSM", "MSQ", "MSBI", "MSSN", "NYEE")) %>%
  mutate(lead_days = CONTACT_DATE - APPT_MADE_DATE) %>%
  mutate(cancel_lead_days = APPT_DTTM - APPT_CANC_DTTM) %>%
  # mutate(lead_days =  as.numeric(difftime(as.Date(APPT_MADE_DATE), as.Date(CONTACT_DATE), units = "days"))) %>%
  # mutate(SPECIALTY_GRP = ifelse(DEPT_SPECIALTY_NAME %in%
  #                                 c("Adolescent Medicine", "Community and Preventive Medicine",
  #                                   "Family Medicine", "Internal Medicine", "Pediatrics", "Geriatrics", "Gerontology", "Urgent Care"), "Primary Care", "Specialty")) %>%
  filter(DERIVED_STATUS_DESC == "Arrived" |
           DERIVED_STATUS_DESC == "No Show" |
           (DERIVED_STATUS_DESC == "Canceled"  & cancel_lead_days <= 1) |
           (DERIVED_STATUS_DESC == "Rescheduled" & cancel_lead_days <= 1)) %>%
  mutate(DERIVED_STATUS_DESC = ifelse(DERIVED_STATUS_DESC == "No Show", "No_Show", DERIVED_STATUS_DESC)) %>%
  mutate(appt_year = year(CONTACT_DATE),
         appt_month = month(CONTACT_DATE),
         appt_week = sql("TRUNC(CONTACT_DATE, 'IW')"),
         appt_day = sql("TRIM(TO_CHAR(CONTACT_DATE, 'DAY'))")) %>%
  mutate(appt_made_year = year(APPT_MADE_DATE),
         appt_made_month = month(APPT_MADE_DATE)) %>%
  mutate(visit_type = ifelse(is.na(VISIT_GROUP_NUM), "ESTABLISHED", "NEW")) %>%
  mutate(lead_14days = ifelse(lead_days <= 14, "lead_14days", "lead_14days_more")) %>%
  filter(CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  filter(CONTACT_DATE <= TO_DATE(date_end , "YYYY-MM-DD HH24:MI:SS")) %>%
  # dplyr::select(SITE, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, DEPARTMENT_ID, PROV_NAME_WID, PAT_ENC_CSN_ID, APPT_STATUS_NAME, CANCEL_LEAD_HOURS, CANCEL_INITIATOR) %>%
  group_by(SITE, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, DEPARTMENT_ID, PROV_ID, NPI, PROV_NAME_WID, PROV_TYPE,
           appt_year, appt_month, appt_day,
           # appt_day, CONTACT_DATE,
           DERIVED_STATUS_DESC) %>%
  summarise(total = n()) %>%
  collect() %>%
  pivot_wider(names_from = c("DERIVED_STATUS_DESC", "appt_day"),
              values_from = total,
              values_fill = 0)


volume_no_show_month <- volume_no_show_month %>%
  mutate(Arrived_AVG = sum(Arrived_MONDAY, Arrived_TUESDAY, Arrived_WEDNESDAY, Arrived_THURSDAY)/4) %>%
  mutate(Arrived_VAR = Arrived_FRIDAY - Arrived_AVG,
         Arrived_VAR_PERC = Arrived_VAR/Arrived_AVG) %>%
  mutate(No_Show_AVG = sum(No_Show_MONDAY, No_Show_TUESDAY, No_Show_WEDNESDAY, No_Show_THURSDAY)/4,
         Canceled_AVG = sum(Canceled_MONDAY, Canceled_TUESDAY, Canceled_WEDNESDAY, Canceled_THURSDAY)/4,
         Rescheduled_AVG = sum(Rescheduled_MONDAY, Rescheduled_TUESDAY, Rescheduled_WEDNESDAY, Rescheduled_THURSDAY)/4) %>%
  mutate(No_Show_Rate_AVG = (No_Show_AVG + Canceled_AVG + Rescheduled_AVG) / (No_Show_AVG + Canceled_AVG + Rescheduled_AVG + Arrived_AVG),
         No_Show_Rate_FRIDAY = (No_Show_FRIDAY + Canceled_FRIDAY + Rescheduled_FRIDAY) / (No_Show_FRIDAY + Canceled_FRIDAY + Rescheduled_FRIDAY + Arrived_FRIDAY))



## Session Count ---------------------------------------------------------------
sessions_month <- access_raw_tbl %>%
  filter(CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  filter(CONTACT_DATE <= TO_DATE(date_end , "YYYY-MM-DD HH24:MI:SS")) %>%
  mutate(cancel_lead_days = APPT_DTTM - APPT_CANC_DTTM) %>%
  filter((CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS") & 
                                    CONTACT_DATE <= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & 
             (DERIVED_STATUS_DESC == "Arrived" |
                DERIVED_STATUS_DESC == "No Show" |
                (DERIVED_STATUS_DESC == "Canceled"  & cancel_lead_days <= 1) |
                (DERIVED_STATUS_DESC == "Rescheduled" & cancel_lead_days <= 1))) |
           (DERIVED_STATUS_DESC == "Scheduled" & (CONTACT_DATE >= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & year(CONTACT_DATE) <= 2026))) %>%
  mutate(appt_year = year(CONTACT_DATE),
         appt_month = month(CONTACT_DATE),
         appt_week = sql("TRUNC(CONTACT_DATE, 'IW')"),
         appt_day = sql("TRIM(TO_CHAR(CONTACT_DATE, 'DAY'))")) %>%
  group_by(DEPARTMENT_ID, PROV_ID, appt_year, appt_month, appt_day, CONTACT_DATE) %>%
  summarise(
    first_appt = min(APPT_DTTM),
    last_appt  = max(APPT_DTTM),
    first_last_appt_hour = (max(APPT_DTTM) - min(APPT_DTTM)) * 24,
    .groups = "drop"
  ) %>%
  mutate(total = ifelse(first_last_appt_hour<2,0, ifelse(first_last_appt_hour<5,1, ifelse(first_last_appt_hour<9,2,3)))) %>%
  group_by(DEPARTMENT_ID, PROV_ID, appt_year, appt_month, appt_day) %>%
  summarise(total = sum(total, na.rm = T)) %>%
  collect() %>%
  mutate(session_cnt = "session_cnt") %>%
  pivot_wider(names_from = c("session_cnt", "appt_day"),
              values_from = total,
              values_fill = 0) %>%
  mutate(session_cnt_AVG = sum(session_cnt_MONDAY + session_cnt_TUESDAY + session_cnt_WEDNESDAY + session_cnt_THURSDAY)/4) %>%
  mutate(session_cnt_VAR = session_cnt_FRIDAY - session_cnt_AVG,
         session_cnt_VAR_PERC = session_cnt_VAR/session_cnt_AVG)



## Physician Count ---------------------------------------------------------------
physicians_month <- access_raw_tbl %>%
  filter(CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  filter(CONTACT_DATE <= TO_DATE(date_end , "YYYY-MM-DD HH24:MI:SS")) %>%
  mutate(cancel_lead_days = APPT_DTTM - APPT_CANC_DTTM) %>%
  filter((CONTACT_DATE >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS") & 
                                    CONTACT_DATE <= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & 
             (DERIVED_STATUS_DESC == "Arrived" |
                DERIVED_STATUS_DESC == "No Show" |
                (DERIVED_STATUS_DESC == "Canceled"  & cancel_lead_days <= 1) |
                (DERIVED_STATUS_DESC == "Rescheduled" & cancel_lead_days <= 1))) |
           (DERIVED_STATUS_DESC == "Scheduled" & (CONTACT_DATE >= TO_DATE(report_run_date, "YYYY-MM-DD HH24:MI:SS") & year(CONTACT_DATE) <= 2026))) %>%
  mutate(appt_year = year(CONTACT_DATE),
         appt_month = month(CONTACT_DATE),
         appt_week = sql("TRUNC(CONTACT_DATE, 'IW')"),
         appt_day = sql("TRIM(TO_CHAR(CONTACT_DATE, 'DAY'))")) %>%
  group_by(DEPARTMENT_ID, PROV_ID, appt_year, appt_month, appt_day) %>%
  summarise(total = n_distinct(PROV_ID)) %>%
  collect() %>%
  mutate(md_cnt = "md_cnt") %>%
  pivot_wider(names_from = c("md_cnt", "appt_day"),
              values_from = total,
              values_fill = 0) %>%
  mutate(md_cnt_AVG = sum(md_cnt_MONDAY + md_cnt_TUESDAY + md_cnt_WEDNESDAY + md_cnt_THURSDAY)/4) %>%
  mutate(md_cnt_VAR = md_cnt_FRIDAY - md_cnt_AVG,
         md_cnt_VAR_PERC = md_cnt_VAR/md_cnt_AVG)


# Unfilled Slots ---------------------------------------------------------------
grp_mapping <- data.frame("SITE" = c("NETWORK", "OTHER", "MSH-MSDFP", "MSUS",
                                        "MSDMG", "MSBI", "MSW", "MSHP", "MSM", "MSH- AMBULATORY CARE",
                                        "NYEE", "MS NOW", "MSQ", "MSSN", "MSB"),
                             "RPT_GRP_SEVNTEEN_C" = c(2, 3,4, 6,
                                                      7, 8, 9, 10, 11, 12,
                                                      13, 14, 15, 19, 38))


unfilled_slots_month <- tbl(conn2, "V_AVAILABILITY") %>%
  # filter(DEPARTMENT_ID == 8001059) %>%
  # filter(PROV_ID == 377151) %>%
  # filter(year(SLOT_BEGIN_TIME) ==  2026) %>%
  # filter(month(SLOT_BEGIN_TIME) == 1) %>%
  # left_join(clarity_ser_2_tbl %>% dplyr::select(PROV_ID, NPI)) %>%
  filter(SLOT_BEGIN_TIME >= TO_DATE(date_start , "YYYY-MM-DD HH24:MI:SS")) %>%
  filter(year(SLOT_BEGIN_TIME) <= 2026) %>%
  mutate(slot_date = sql("TRUNC(SLOT_BEGIN_TIME)"),
         slot_year = year(SLOT_BEGIN_TIME),
         slot_month = month(SLOT_BEGIN_TIME),
         slot_day = sql("TO_CHAR(TRUNC(SLOT_BEGIN_TIME), 'FMDAY')"),
         slot_week = sql("TRUNC(SLOT_BEGIN_TIME, 'IW')")) %>%
  filter(TIME_HELD_YN == "N" | TIME_UNAVAIL_YN == "N") %>%
  filter(SLOT_LENGTH >= 10) %>%
  filter(as.numeric(SLOT_HOUR) >= 7 & as.numeric(SLOT_HOUR) <= 21) %>%

  # Exclude any dates with 0 appts scheduled (false template)
  group_by(DEPARTMENT_ID, PROV_ID, slot_date) %>%
  mutate(apts_scheduled = sum(NUM_APTS_SCHEDULED, na.rm = T)) %>%
  filter(apts_scheduled > 0) %>%
  filter(APPT_NUMBER == 0) %>%
  filter(ORG_REG_OPENINGS - NUM_APTS_SCHEDULED > 0) %>%

  group_by(DEPARTMENT_ID, PROV_ID, slot_year, slot_month, slot_day) %>%
  summarise(total = n()) %>%
  collect() %>%
  mutate(unfilled_cnt = "unfilled_cnt") %>%
  pivot_wider(names_from = c("unfilled_cnt", "slot_day"),
              values_from = total,
              values_fill = 0) %>%
  mutate(unfilled_cnt_AVG = sum(unfilled_cnt_MONDAY + unfilled_cnt_TUESDAY + unfilled_cnt_WEDNESDAY + unfilled_cnt_THURSDAY)/4) %>%
  mutate(unfilled_cnt_VAR = unfilled_cnt_FRIDAY - unfilled_cnt_AVG,
         unfilled_cnt_VAR_PERC = unfilled_cnt_VAR/unfilled_cnt_AVG)




## Merged Data -----------------------------------------------------------------
merged_data_month <- full_join(scheduled_volume_month, volume_no_show_month)
merged_data_month <- full_join(merged_data_month, sessions_month)
merged_data_month <- full_join(merged_data_month, physicians_month)
merged_data_month <- left_join(merged_data_month, unfilled_slots_month,
                         by = c("DEPARTMENT_ID" = "DEPARTMENT_ID",
                                "PROV_ID" = "PROV_ID",
                                "appt_year" = "slot_year",
                                "appt_month" = "slot_month"))


merged_data_month <- merged_data_month %>%
  left_join(location %>% dplyr::select(DEPARTMENT_ID, STANDARD_ADDRESS)) %>%
  # left_join(holidays %>% dplyr::select(holiday, week_start),
  #           by = c("appt_" = "week_start")) %>%
  # mutate(appt_week = as.character(appt_week)) %>%
  arrange(appt_year, appt_month, STANDARD_ADDRESS, DEPT_SPECIALTY_NAME, DEPARTMENT_NAME, PROV_TYPE, PROV_NAME_WID)

# require(openxlsx)
# write.xlsx(friday_data, "Friday Volume_040926.xlsx")


col_order <- c("appt_year", "appt_month", 
               "SITE", "STANDARD_ADDRESS",  "DEPT_SPECIALTY_NAME", "DEPARTMENT_NAME", "DEPARTMENT_ID", "PROV_TYPE", "PROV_ID", "NPI", "PROV_NAME_WID",
               "Scheduled_AVG", "Scheduled_MONDAY", "Scheduled_TUESDAY", "Scheduled_WEDNESDAY", "Scheduled_THURSDAY", "Scheduled_FRIDAY", "Scheduled_SATURDAY", "Scheduled_SUNDAY",
               "Scheduled_VAR", "Scheduled_VAR_PERC",
               "Arrived_AVG", "Arrived_MONDAY", "Arrived_TUESDAY", "Arrived_WEDNESDAY", "Arrived_THURSDAY", "Arrived_FRIDAY", "Arrived_SATURDAY", "Arrived_SUNDAY",
               "Arrived_VAR", "Arrived_VAR_PERC",
               "md_cnt_AVG", "md_cnt_MONDAY", "md_cnt_TUESDAY", "md_cnt_WEDNESDAY", "md_cnt_THURSDAY", "md_cnt_FRIDAY", "md_cnt_SATURDAY", "md_cnt_SUNDAY",
               "md_cnt_VAR", "md_cnt_VAR_PERC",
               "session_cnt_AVG", "session_cnt_MONDAY", "session_cnt_TUESDAY", "session_cnt_WEDNESDAY", "session_cnt_THURSDAY",
               "session_cnt_FRIDAY", "session_cnt_SATURDAY", "session_cnt_SUNDAY",
               "session_cnt_VAR", "session_cnt_VAR_PERC",
               "unfilled_cnt_AVG", "unfilled_cnt_MONDAY", "unfilled_cnt_TUESDAY", "unfilled_cnt_WEDNESDAY", "unfilled_cnt_THURSDAY",
               "unfilled_cnt_FRIDAY", "unfilled_cnt_SATURDAY", "unfilled_cnt_SUNDAY",
               "unfilled_cnt_VAR", "unfilled_cnt_VAR_PERC",
               "Canceled_AVG", "Canceled_MONDAY", "Canceled_TUESDAY", "Canceled_WEDNESDAY", "Canceled_THURSDAY", "Canceled_FRIDAY", "Canceled_SATURDAY", "Canceled_SUNDAY",
               "Rescheduled_AVG", "Rescheduled_MONDAY", "Rescheduled_TUESDAY", "Rescheduled_WEDNESDAY", "Rescheduled_THURSDAY",
               "Rescheduled_FRIDAY", "Rescheduled_SATURDAY", "Rescheduled_SUNDAY",
               "No_Show_AVG", "No_Show_MONDAY", "No_Show_TUESDAY", "No_Show_WEDNESDAY", "No_Show_THURSDAY", "No_Show_FRIDAY", "No_Show_SATURDAY", "No_Show_SUNDAY",
               "No_Show_Rate_AVG", "No_Show_Rate_FRIDAY")


# setdiff(col_order, colnames(merged_data))


merged_data_month <- merged_data_month %>%
  dplyr::select(col_order)

```




# Friday Volume Performance {.tabset .tabset-fade .tabset-pills}
*Report run date: `r report_run_date`*<br/>
______________________________________________________________________________________________________________________________
<br/>
<br/>


## Performance by Week (Physicians Only)
*Performance by Week excludes any weeks with Mount Sinai observed holidays*<br/>
```{r KPI Tracker}

htmltools::browsable(
  tagList(
    tags$button(
      tagList(fontawesome::fa("download"), "Download Table"),
      onclick = "Reactable.downloadDataCSV('performance-tracker', 'Volume Rebuild Progress')"
    ),

# htmltools::browsable(
#   tagList(
#     div(tags$label("Summary by", `for` = "access-roi")),
#     tags$select(
#       id = "access-roi",
#       onchange = "Reactable.setGroupBy('access-metrics', this.value ? [this.value] : [])",
#       tags$option("None", value = ""),
#       lapply(c("Year", "Month"), tags$option)
#     ),
# 
#     tags$hr("aria-hidden" = "true"),
    
reactable(
  merged_data %>%
    filter(SITE %in% c("MSB", "MSBI", "MSDMG", "MSH- AMBULATORY CARE", "MSH-MSDFP", "MSM", "MSQ",
                       "MSUS", "MSW", "NETWORK", "NYEE", "MSB")) %>%
    filter(PROV_TYPE == "Physician") %>%
    filter(is.na(holiday)),
  elementId = "performance-tracker",
  # elementId = "referral-vol-download-table",
  style = list(fontFamily = 'Calibri',
                 fontSize = '14px'),
    defaultColDef = colDef(align = "left",
                           headerStyle = list(fontWeight = "Bold", fontSize = "14px"),
                           headerClass = "bar-sort-header"),
  # RowStyle = function(index) {
  #           if (index %in% c(nrow(referral_vol_site_data_mshs))) {
  #             list(`border-top` = "2px solid rgb(184,184,184)",
  #                  fontWeight = "Bold")
  #           }
  #         },
    highlight = TRUE,
    # filterable = TRUE,
    pagination = FALSE,
    # height = 800,
    wrap = TRUE,
  searchable = TRUE,

  groupBy = c("appt_week","SITE","STANDARD_ADDRESS","DEPT_SPECIALTY_NAME","DEPARTMENT_NAME","PROV_TYPE"),

  columnGroups = list(
    colGroup(name = "", columns = c("appt_week"),
             headerStyle = list(color = "black", fontSize = "15px"),
             sticky = "left"),
    colGroup(name = "", columns = c("SITE","STANDARD_ADDRESS","DEPT_SPECIALTY_NAME","DEPARTMENT_NAME","PROV_TYPE", "PROV_NAME_WID"),
             headerStyle = list(color = "black", fontSize = "15px")),
    colGroup(name = paste0("Scheduled Visits"),
             columns = c("Scheduled_AVG", "Scheduled_FRIDAY", "Scheduled_VAR", "Scheduled_VAR_PERC"),
             headerStyle = list(background = "#7f7f7f", color = "white", fontSize = "15px")),
    colGroup(name = paste0("Arrived Visits"),
             columns = c("Arrived_AVG", "Arrived_FRIDAY", "Arrived_VAR", "Arrived_VAR_PERC"),
             headerStyle = list(background = "#7f7f7f", color = "white", fontSize = "15px")),
    colGroup(name = paste0("Practicing Physicians"),
             columns = c("md_cnt_AVG", "md_cnt_FRIDAY", "md_cnt_VAR", "md_cnt_VAR_PERC"),
             headerStyle = list(background = "#212070", color = "white", fontSize = "15px")),
    colGroup(name = paste0("Sessions"),
             columns = c("session_cnt_AVG", "session_cnt_FRIDAY", "session_cnt_VAR", "session_cnt_VAR_PERC"),
             headerStyle = list(background = "#d80b8c", color = "white", fontSize = "15px")),
    colGroup(name = paste0("Unfilled Slots"),
             columns = c("unfilled_cnt_AVG", "unfilled_cnt_FRIDAY", "unfilled_cnt_VAR", "unfilled_cnt_VAR_PERC"),
             headerStyle = list(background = "#00aeef", color = "white", fontSize = "15px")),
    colGroup(name = paste0("No Show Rate"),
             columns = c("No_Show_Rate_AVG", "No_Show_Rate_FRIDAY"),
             headerStyle = list(background = "#a5a7a5", color = "white", fontSize = "15px"))
    ),

  columns = list(
# 
#      appt_year = colDef(
#       name = "Year",
#       maxWidth = 100),
     
     appt_week = colDef(
      name = "Week",
      minWidth = 200),
     
     SITE = colDef(
      name = "Site",
      minWidth = 200),
     
     STANDARD_ADDRESS = colDef(
      name = "Location",
      minWidth = 400),
     
     DEPT_SPECIALTY_NAME = colDef(
      name = "Specialty",
      minWidth = 200),
     
     DEPARTMENT_NAME = colDef(
      name = "Department",
      minWidth = 200),
     
     PROV_TYPE = colDef(
      name = "Provider Type",
      minWidth = 200),
     
     PROV_NAME_WID = colDef(
      name = "Provider",
      minWidth = 200),
     
     
     Scheduled_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),
     
     Scheduled_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),
     
     Scheduled_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalScheduled_MONDAY = 0
        let totalScheduled_TUESDAY = 0
        let totalScheduled_WEDNESDAY = 0
        let totalScheduled_THURSDAY = 0
        let totalScheduled_FRIDAY = 0
        rows.forEach(function(row) {
          totalScheduled_MONDAY += row['Scheduled_MONDAY']
          totalScheduled_TUESDAY += row['Scheduled_TUESDAY']
          totalScheduled_WEDNESDAY += row['Scheduled_WEDNESDAY']
          totalScheduled_THURSDAY += row['Scheduled_THURSDAY']
          totalScheduled_FRIDAY += row['Scheduled_FRIDAY']
        })
        return (totalScheduled_FRIDAY) - ((totalScheduled_MONDAY + totalScheduled_TUESDAY + totalScheduled_WEDNESDAY + totalScheduled_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['Scheduled_VAR']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),
     
     Scheduled_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalScheduled_MONDAY = 0
        let totalScheduled_TUESDAY = 0
        let totalScheduled_WEDNESDAY = 0
        let totalScheduled_THURSDAY = 0
        let totalScheduled_FRIDAY = 0
        rows.forEach(function(row) {
          totalScheduled_MONDAY += row['Scheduled_MONDAY']
          totalScheduled_TUESDAY += row['Scheduled_TUESDAY']
          totalScheduled_WEDNESDAY += row['Scheduled_WEDNESDAY']
          totalScheduled_THURSDAY += row['Scheduled_THURSDAY']
          totalScheduled_FRIDAY += row['Scheduled_FRIDAY']
        })
        return (totalScheduled_FRIDAY - ((totalScheduled_MONDAY + totalScheduled_TUESDAY + totalScheduled_WEDNESDAY + totalScheduled_THURSDAY)/4)) /
        ((totalScheduled_MONDAY + totalScheduled_TUESDAY + totalScheduled_WEDNESDAY + totalScheduled_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['Scheduled_VAR_PERC']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),
     
     
     Arrived_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),
     
     Arrived_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),
     
     Arrived_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalArrived_MONDAY = 0
        let totalArrived_TUESDAY = 0
        let totalArrived_WEDNESDAY = 0
        let totalArrived_THURSDAY = 0
        let totalArrived_FRIDAY = 0
        rows.forEach(function(row) {
          totalArrived_MONDAY += row['Arrived_MONDAY']
          totalArrived_TUESDAY += row['Arrived_TUESDAY']
          totalArrived_WEDNESDAY += row['Arrived_WEDNESDAY']
          totalArrived_THURSDAY += row['Arrived_THURSDAY']
          totalArrived_FRIDAY += row['Arrived_FRIDAY']
        })
        return (totalArrived_FRIDAY) - ((totalArrived_MONDAY + totalArrived_TUESDAY + totalArrived_WEDNESDAY + totalArrived_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['Arrived_VAR']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),
     
     Arrived_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalArrived_MONDAY = 0
        let totalArrived_TUESDAY = 0
        let totalArrived_WEDNESDAY = 0
        let totalArrived_THURSDAY = 0
        let totalArrived_FRIDAY = 0
        rows.forEach(function(row) {
          totalArrived_MONDAY += row['Arrived_MONDAY']
          totalArrived_TUESDAY += row['Arrived_TUESDAY']
          totalArrived_WEDNESDAY += row['Arrived_WEDNESDAY']
          totalArrived_THURSDAY += row['Arrived_THURSDAY']
          totalArrived_FRIDAY += row['Arrived_FRIDAY']
        })
        return (totalArrived_FRIDAY - ((totalArrived_MONDAY + totalArrived_TUESDAY + totalArrived_WEDNESDAY + totalArrived_THURSDAY)/4)) /
        ((totalArrived_MONDAY + totalArrived_TUESDAY + totalArrived_WEDNESDAY + totalArrived_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['Arrived_VAR_PERC']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),



     md_cnt_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#212070", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     md_cnt_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#212070", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     md_cnt_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#212070", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalmd_cnt_MONDAY = 0
        let totalmd_cnt_TUESDAY = 0
        let totalmd_cnt_WEDNESDAY = 0
        let totalmd_cnt_THURSDAY = 0
        let totalmd_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalmd_cnt_MONDAY += row['md_cnt_MONDAY']
          totalmd_cnt_TUESDAY += row['md_cnt_TUESDAY']
          totalmd_cnt_WEDNESDAY += row['md_cnt_WEDNESDAY']
          totalmd_cnt_THURSDAY += row['md_cnt_THURSDAY']
          totalmd_cnt_FRIDAY += row['md_cnt_FRIDAY']
        })
        return (totalmd_cnt_FRIDAY - ((totalmd_cnt_MONDAY + totalmd_cnt_TUESDAY + totalmd_cnt_WEDNESDAY + totalmd_cnt_THURSDAY)/4)) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['md_cnt_VAR']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),

     md_cnt_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#212070", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
       let totalmd_cnt_MONDAY = 0
        let totalmd_cnt_TUESDAY = 0
        let totalmd_cnt_WEDNESDAY = 0
        let totalmd_cnt_THURSDAY = 0
        let totalmd_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalmd_cnt_MONDAY += row['md_cnt_MONDAY']
          totalmd_cnt_TUESDAY += row['md_cnt_TUESDAY']
          totalmd_cnt_WEDNESDAY += row['md_cnt_WEDNESDAY']
          totalmd_cnt_THURSDAY += row['md_cnt_THURSDAY']
          totalmd_cnt_FRIDAY += row['md_cnt_FRIDAY']
        })
        return (totalmd_cnt_FRIDAY - ((totalmd_cnt_MONDAY + totalmd_cnt_TUESDAY + totalmd_cnt_WEDNESDAY + totalmd_cnt_THURSDAY)/4)) /
        ((totalmd_cnt_MONDAY + totalmd_cnt_TUESDAY + totalmd_cnt_WEDNESDAY + totalmd_cnt_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['md_cnt_VAR_PERC']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),



     session_cnt_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#d80b8c", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     session_cnt_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#d80b8c", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     session_cnt_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#d80b8c", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalsession_cnt_MONDAY = 0
        let totalsession_cnt_TUESDAY = 0
        let totalsession_cnt_WEDNESDAY = 0
        let totalsession_cnt_THURSDAY = 0
        let totalsession_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalsession_cnt_MONDAY += row['session_cnt_MONDAY']
          totalsession_cnt_TUESDAY += row['session_cnt_TUESDAY']
          totalsession_cnt_WEDNESDAY += row['session_cnt_WEDNESDAY']
          totalsession_cnt_THURSDAY += row['session_cnt_THURSDAY']
          totalsession_cnt_FRIDAY += row['session_cnt_FRIDAY']
        })
        return (totalsession_cnt_FRIDAY - ((totalsession_cnt_MONDAY + totalsession_cnt_TUESDAY + totalsession_cnt_WEDNESDAY + totalsession_cnt_THURSDAY)/4)) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['session_cnt_VAR']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),

     session_cnt_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#d80b8c", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalsession_cnt_MONDAY = 0
        let totalsession_cnt_TUESDAY = 0
        let totalsession_cnt_WEDNESDAY = 0
        let totalsession_cnt_THURSDAY = 0
        let totalsession_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalsession_cnt_MONDAY += row['session_cnt_MONDAY']
          totalsession_cnt_TUESDAY += row['session_cnt_TUESDAY']
          totalsession_cnt_WEDNESDAY += row['session_cnt_WEDNESDAY']
          totalsession_cnt_THURSDAY += row['session_cnt_THURSDAY']
          totalsession_cnt_FRIDAY += row['session_cnt_FRIDAY']
        })
        return (totalsession_cnt_FRIDAY - ((totalsession_cnt_MONDAY + totalsession_cnt_TUESDAY + totalsession_cnt_WEDNESDAY + totalsession_cnt_THURSDAY)/4)) /
        ((totalsession_cnt_MONDAY + totalsession_cnt_TUESDAY + totalsession_cnt_WEDNESDAY + totalsession_cnt_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['session_cnt_VAR_PERC']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),


     unfilled_cnt_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#00aeef", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     unfilled_cnt_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#00aeef", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     unfilled_cnt_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#00aeef", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalunfilled_cnt_MONDAY = 0
        let totalunfilled_cnt_TUESDAY = 0
        let totalunfilled_cnt_WEDNESDAY = 0
        let totalunfilled_cnt_THURSDAY = 0
        let totalunfilled_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalunfilled_cnt_MONDAY += row['unfilled_cnt_MONDAY']
          totalunfilled_cnt_TUESDAY += row['unfilled_cnt_TUESDAY']
          totalunfilled_cnt_WEDNESDAY += row['unfilled_cnt_WEDNESDAY']
          totalunfilled_cnt_THURSDAY += row['unfilled_cnt_THURSDAY']
          totalunfilled_cnt_FRIDAY += row['unfilled_cnt_FRIDAY']
        })
        return (totalunfilled_cnt_FRIDAY - ((totalunfilled_cnt_MONDAY + totalunfilled_cnt_TUESDAY + totalunfilled_cnt_WEDNESDAY + totalunfilled_cnt_THURSDAY)/4)) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['unfilled_cnt_VAR']
        if (value > 0) {
          var color = '#e00000'
        } else {
          var color = '#008000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),

     unfilled_cnt_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#00aeef", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalunfilled_cnt_MONDAY = 0
        let totalunfilled_cnt_TUESDAY = 0
        let totalunfilled_cnt_WEDNESDAY = 0
        let totalunfilled_cnt_THURSDAY = 0
        let totalunfilled_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalunfilled_cnt_MONDAY += row['unfilled_cnt_MONDAY']
          totalunfilled_cnt_TUESDAY += row['unfilled_cnt_TUESDAY']
          totalunfilled_cnt_WEDNESDAY += row['unfilled_cnt_WEDNESDAY']
          totalunfilled_cnt_THURSDAY += row['unfilled_cnt_THURSDAY']
          totalunfilled_cnt_FRIDAY += row['unfilled_cnt_FRIDAY']
        })
        return (totalunfilled_cnt_FRIDAY - ((totalunfilled_cnt_MONDAY + totalunfilled_cnt_TUESDAY + totalunfilled_cnt_WEDNESDAY + totalunfilled_cnt_THURSDAY)/4)) /
        ((totalunfilled_cnt_MONDAY + totalunfilled_cnt_TUESDAY + totalunfilled_cnt_WEDNESDAY + totalunfilled_cnt_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['unfilled_cnt_VAR_PERC']
        if (value > 0) {
          var color = '#e00000'
        } else {
          var color = '#008000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),



No_Show_Rate_AVG = colDef(
 name = "Mon-Thu Avg",
 maxWidth = 80,
 headerStyle = list(background = "#a5a7a5", color = "white", fontWeight = "Bold", fontSize = "14px"),
 aggregate = JS("function(values, rows) {
   let totalNo_Show_MONDAY = 0
   let totalNo_Show_TUESDAY = 0
   let totalNo_Show_WEDNESDAY = 0
   let totalNo_Show_THURSDAY = 0
   let totalCanceled_MONDAY = 0
   let totalCanceled_TUESDAY = 0
   let totalCanceled_WEDNESDAY = 0
   let totalCanceled_THURSDAY = 0
   let totalRescheduled_MONDAY = 0
   let totalRescheduled_TUESDAY = 0
   let totalRescheduled_WEDNESDAY = 0
   let totalRescheduled_THURSDAY = 0
   let totalArrived_MONDAY = 0
   let totalArrived_TUESDAY = 0
   let totalArrived_WEDNESDAY = 0
   let totalArrived_THURSDAY = 0
   rows.forEach(function(row) {
     totalNo_Show_MONDAY += row['No_Show_MONDAY']
     totalNo_Show_TUESDAY += row['No_Show_TUESDAY']
     totalNo_Show_WEDNESDAY += row['No_Show_WEDNESDAY']
     totalNo_Show_THURSDAY += row['No_Show_THURSDAY']
     totalCanceled_MONDAY += row['Canceled_MONDAY']
     totalCanceled_TUESDAY += row['Canceled_TUESDAY']
     totalCanceled_WEDNESDAY += row['Canceled_WEDNESDAY']
     totalCanceled_THURSDAY += row['Canceled_THURSDAY']
     totalRescheduled_MONDAY += row['Rescheduled_MONDAY']
     totalRescheduled_TUESDAY += row['Rescheduled_TUESDAY']
     totalRescheduled_WEDNESDAY += row['Rescheduled_WEDNESDAY']
     totalRescheduled_THURSDAY += row['Rescheduled_THURSDAY']
     totalArrived_MONDAY += row['Arrived_MONDAY']
     totalArrived_TUESDAY += row['Arrived_TUESDAY']
     totalArrived_WEDNESDAY += row['Arrived_WEDNESDAY']
     totalArrived_THURSDAY += row['Arrived_THURSDAY']
   })
   return (totalNo_Show_MONDAY + totalNo_Show_TUESDAY + totalNo_Show_WEDNESDAY + totalNo_Show_THURSDAY +
           totalCanceled_MONDAY + totalCanceled_TUESDAY + totalCanceled_WEDNESDAY + totalCanceled_THURSDAY +
           totalRescheduled_MONDAY + totalRescheduled_TUESDAY + totalRescheduled_WEDNESDAY + totalRescheduled_THURSDAY) /
           (totalNo_Show_MONDAY + totalNo_Show_TUESDAY + totalNo_Show_WEDNESDAY + totalNo_Show_THURSDAY +
           totalCanceled_MONDAY + totalCanceled_TUESDAY + totalCanceled_WEDNESDAY + totalCanceled_THURSDAY +
           totalRescheduled_MONDAY + totalRescheduled_TUESDAY + totalRescheduled_WEDNESDAY + totalRescheduled_THURSDAY +
           totalArrived_MONDAY + totalArrived_TUESDAY + totalArrived_WEDNESDAY + totalArrived_THURSDAY) || '-'

 }"),
 style = JS("function(rowInfo) {
   var value = rowInfo.row['No_Show_Rate_AVG']
   if (value > 0) {
     var color = '#e00000'
   } else {
     var color = '#008000'
   }
   return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
 }"),
 format = colFormat(percent = TRUE, digits = 1)),


     No_Show_Rate_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#a5a7a5", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalNo_Show_FRIDAY = 0
        let totalCanceled_FRIDAY = 0
        let totalRescheduled_FRIDAY = 0
        let totalArrived_FRIDAY = 0
        rows.forEach(function(row) {
          totalNo_Show_FRIDAY += row['No_Show_FRIDAY']
          totalCanceled_FRIDAY += row['Canceled_FRIDAY']
          totalRescheduled_FRIDAY += row['Rescheduled_FRIDAY']
          totalArrived_FRIDAY += row['Arrived_FRIDAY']
        })
        return (totalNo_Show_FRIDAY + totalCanceled_FRIDAY + totalRescheduled_FRIDAY) /
        (totalNo_Show_FRIDAY + totalCanceled_FRIDAY + totalRescheduled_FRIDAY + totalArrived_FRIDAY) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['No_Show_Rate_FRIDAY']
        if (value > 0) {
          var color = '#e00000'
        } else {
          var color = ' #008000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),

     appt_year = colDef(show =F),
     holiday = colDef(show =F),
     DEPARTMENT_ID = colDef(show =F),
     PROV_ID = colDef(show =F),
     NPI = colDef(show =F),
     Scheduled_MONDAY = colDef(show =F),
     Scheduled_TUESDAY = colDef(show =F),
     Scheduled_WEDNESDAY = colDef(show =F),
     Scheduled_THURSDAY = colDef(show =F),
     Scheduled_SATURDAY = colDef(show =F),
     Scheduled_SUNDAY = colDef(show =F),
     Arrived_MONDAY = colDef(show =F),
     Arrived_TUESDAY = colDef(show =F),
     Arrived_WEDNESDAY = colDef(show =F),
     Arrived_THURSDAY = colDef(show =F),
     Arrived_SATURDAY = colDef(show =F),
     Arrived_SUNDAY = colDef(show =F),
     md_cnt_MONDAY = colDef(show =F),
     md_cnt_TUESDAY = colDef(show =F),
     md_cnt_WEDNESDAY = colDef(show =F),
     md_cnt_THURSDAY = colDef(show =F),
     md_cnt_SATURDAY = colDef(show =F),
     md_cnt_SUNDAY = colDef(show =F),
     session_cnt_MONDAY = colDef(show =F),
     session_cnt_TUESDAY = colDef(show =F),
     session_cnt_WEDNESDAY = colDef(show =F),
     session_cnt_THURSDAY = colDef(show =F),
     session_cnt_SATURDAY = colDef(show =F),
     session_cnt_SUNDAY = colDef(show =F),
     unfilled_cnt_MONDAY = colDef(show =F),
     unfilled_cnt_TUESDAY = colDef(show =F),
     unfilled_cnt_WEDNESDAY = colDef(show =F),
     unfilled_cnt_THURSDAY = colDef(show =F),
     unfilled_cnt_SATURDAY = colDef(show =F),
     unfilled_cnt_SUNDAY = colDef(show =F),
     Canceled_MONDAY = colDef(show =F),
     Canceled_TUESDAY = colDef(show =F),
     Canceled_WEDNESDAY = colDef(show =F),
     Canceled_THURSDAY = colDef(show =F),
     Canceled_FRIDAY = colDef(show =F),
     Canceled_SATURDAY = colDef(show =F),
     Canceled_SUNDAY = colDef(show =F),
     Canceled_AVG = colDef(show =F),
     Rescheduled_MONDAY = colDef(show =F),
     Rescheduled_TUESDAY = colDef(show =F),
     Rescheduled_WEDNESDAY = colDef(show =F),
     Rescheduled_THURSDAY = colDef(show =F),
     Rescheduled_FRIDAY = colDef(show =F),
     Rescheduled_SATURDAY = colDef(show =F),
     Rescheduled_SUNDAY = colDef(show =F),
     Rescheduled_AVG = colDef(show =F),
     No_Show_MONDAY = colDef(show =F),
     No_Show_TUESDAY = colDef(show =F),
     No_Show_WEDNESDAY = colDef(show =F),
     No_Show_THURSDAY = colDef(show =F),
     No_Show_FRIDAY = colDef(show =F),
     No_Show_SATURDAY = colDef(show =F),
     No_Show_SUNDAY = colDef(show =F),
     No_Show_AVG = colDef(show =F)
     
  ) # Close Columns

  ) # Close Reactable
) # Close Taglist
) # Close htmltools


```


## Performance by Month (Physicians Only)
*Performance by Week includes all weeks*<br/>
```{r KPI Tracker by Month}

htmltools::browsable(
  tagList(
    tags$button(
      tagList(fontawesome::fa("download"), "Download Table"),
      onclick = "Reactable.downloadDataCSV('performance-tracker-month', 'Volume Rebuild Progress')"
    ),

# htmltools::browsable(
#   tagList(
#     div(tags$label("Summary by", `for` = "access-roi")),
#     tags$select(
#       id = "access-roi",
#       onchange = "Reactable.setGroupBy('access-metrics', this.value ? [this.value] : [])",
#       tags$option("None", value = ""),
#       lapply(c("Year", "Month"), tags$option)
#     ),
#
#     tags$hr("aria-hidden" = "true"),

reactable(
  merged_data_month %>%
    filter(SITE %in% c("MSB", "MSBI", "MSDMG", "MSH- AMBULATORY CARE", "MSH-MSDFP", "MSM", "MSQ",
                       "MSUS", "MSW", "NETWORK", "NYEE", "MSB")) %>%
    filter(PROV_TYPE == "Physician"),
  elementId = "performance-tracker-month",
  # elementId = "referral-vol-download-table",
  style = list(fontFamily = 'Calibri',
                 fontSize = '14px'),
    defaultColDef = colDef(align = "left",
                           headerStyle = list(fontWeight = "Bold", fontSize = "14px"),
                           headerClass = "bar-sort-header"),
  # RowStyle = function(index) {
  #           if (index %in% c(nrow(referral_vol_site_data_mshs))) {
  #             list(`border-top` = "2px solid rgb(184,184,184)",
  #                  fontWeight = "Bold")
  #           }
  #         },
    highlight = TRUE,
    # filterable = TRUE,
    pagination = FALSE,
    # height = 800,
    wrap = TRUE,
  searchable = TRUE,

  groupBy = c("appt_year", "appt_month","SITE","STANDARD_ADDRESS","DEPT_SPECIALTY_NAME","DEPARTMENT_NAME","PROV_TYPE"),

  columnGroups = list(
    colGroup(name = "", columns = c("appt_year", "appt_month"),
             headerStyle = list(color = "black", fontSize = "15px"),
             sticky = "left"),
    colGroup(name = "", columns = c("SITE","STANDARD_ADDRESS","DEPT_SPECIALTY_NAME","DEPARTMENT_NAME","PROV_TYPE", "PROV_NAME_WID"),
             headerStyle = list(color = "black", fontSize = "15px")),
    colGroup(name = paste0("Scheduled Visits"),
             columns = c("Scheduled_AVG", "Scheduled_FRIDAY", "Scheduled_VAR", "Scheduled_VAR_PERC")),
    colGroup(name = paste0("Arrived Visits"),
             columns = c("Arrived_AVG", "Arrived_FRIDAY", "Arrived_VAR", "Arrived_VAR_PERC"),
             headerStyle = list(background = "#7f7f7f", color = "white", fontSize = "15px")),
    colGroup(name = paste0("Practicing Physicians"),
             columns = c("md_cnt_AVG", "md_cnt_FRIDAY", "md_cnt_VAR", "md_cnt_VAR_PERC"),
             headerStyle = list(background = "#212070", color = "white", fontSize = "15px")),
    colGroup(name = paste0("Sessions"),
             columns = c("session_cnt_AVG", "session_cnt_FRIDAY", "session_cnt_VAR", "session_cnt_VAR_PERC"),
             headerStyle = list(background = "#d80b8c", color = "white", fontSize = "15px")),
    colGroup(name = paste0("Unfilled Slots"),
             columns = c("unfilled_cnt_AVG", "unfilled_cnt_FRIDAY", "unfilled_cnt_VAR", "unfilled_cnt_VAR_PERC"),
             headerStyle = list(background = "#00aeef", color = "white", fontSize = "15px")),
    colGroup(name = paste0("No Show Rate"),
             columns = c("No_Show_Rate_AVG", "No_Show_Rate_FRIDAY"),
             headerStyle = list(background = "#a5a7a5", color = "white", fontSize = "15px"))
    ),

  columns = list(

     appt_year = colDef(
      name = "Year",
      maxWidth = 100),

     appt_month = colDef(
      name = "Month",
      maxWidth = 200),

     SITE = colDef(
      name = "Site",
      minWidth = 200),

     STANDARD_ADDRESS = colDef(
      name = "Location",
      minWidth = 400),

     DEPT_SPECIALTY_NAME = colDef(
      name = "Specialty",
      minWidth = 200),

     DEPARTMENT_NAME = colDef(
      name = "Department",
      minWidth = 200),

     PROV_TYPE = colDef(
      name = "Provider Type",
      minWidth = 200),

     PROV_NAME_WID = colDef(
      name = "Provider",
      minWidth = 200),
     
     
     Scheduled_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     Scheduled_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     Scheduled_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalScheduled_MONDAY = 0
        let totalScheduled_TUESDAY = 0
        let totalScheduled_WEDNESDAY = 0
        let totalScheduled_THURSDAY = 0
        let totalScheduled_FRIDAY = 0
        rows.forEach(function(row) {
          totalScheduled_MONDAY += row['Scheduled_MONDAY']
          totalScheduled_TUESDAY += row['Scheduled_TUESDAY']
          totalScheduled_WEDNESDAY += row['Scheduled_WEDNESDAY']
          totalScheduled_THURSDAY += row['Scheduled_THURSDAY']
          totalScheduled_FRIDAY += row['Scheduled_FRIDAY']
        })
        return (totalScheduled_FRIDAY) - ((totalScheduled_MONDAY + totalScheduled_TUESDAY + totalScheduled_WEDNESDAY + totalScheduled_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['Scheduled_VAR']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),

     Scheduled_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalScheduled_MONDAY = 0
        let totalScheduled_TUESDAY = 0
        let totalScheduled_WEDNESDAY = 0
        let totalScheduled_THURSDAY = 0
        let totalScheduled_FRIDAY = 0
        rows.forEach(function(row) {
          totalScheduled_MONDAY += row['Scheduled_MONDAY']
          totalScheduled_TUESDAY += row['Scheduled_TUESDAY']
          totalScheduled_WEDNESDAY += row['Scheduled_WEDNESDAY']
          totalScheduled_THURSDAY += row['Scheduled_THURSDAY']
          totalScheduled_FRIDAY += row['Scheduled_FRIDAY']
        })
        return (totalScheduled_FRIDAY - ((totalScheduled_MONDAY + totalScheduled_TUESDAY + totalScheduled_WEDNESDAY + totalScheduled_THURSDAY)/4)) /
        ((totalScheduled_MONDAY + totalScheduled_TUESDAY + totalScheduled_WEDNESDAY + totalScheduled_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['Scheduled_VAR_PERC']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),

     

     Arrived_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     Arrived_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     Arrived_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalArrived_MONDAY = 0
        let totalArrived_TUESDAY = 0
        let totalArrived_WEDNESDAY = 0
        let totalArrived_THURSDAY = 0
        let totalArrived_FRIDAY = 0
        rows.forEach(function(row) {
          totalArrived_MONDAY += row['Arrived_MONDAY']
          totalArrived_TUESDAY += row['Arrived_TUESDAY']
          totalArrived_WEDNESDAY += row['Arrived_WEDNESDAY']
          totalArrived_THURSDAY += row['Arrived_THURSDAY']
          totalArrived_FRIDAY += row['Arrived_FRIDAY']
        })
        return (totalArrived_FRIDAY) - ((totalArrived_MONDAY + totalArrived_TUESDAY + totalArrived_WEDNESDAY + totalArrived_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['Arrived_VAR']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),

     Arrived_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#7f7f7f", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalArrived_MONDAY = 0
        let totalArrived_TUESDAY = 0
        let totalArrived_WEDNESDAY = 0
        let totalArrived_THURSDAY = 0
        let totalArrived_FRIDAY = 0
        rows.forEach(function(row) {
          totalArrived_MONDAY += row['Arrived_MONDAY']
          totalArrived_TUESDAY += row['Arrived_TUESDAY']
          totalArrived_WEDNESDAY += row['Arrived_WEDNESDAY']
          totalArrived_THURSDAY += row['Arrived_THURSDAY']
          totalArrived_FRIDAY += row['Arrived_FRIDAY']
        })
        return (totalArrived_FRIDAY - ((totalArrived_MONDAY + totalArrived_TUESDAY + totalArrived_WEDNESDAY + totalArrived_THURSDAY)/4)) /
        ((totalArrived_MONDAY + totalArrived_TUESDAY + totalArrived_WEDNESDAY + totalArrived_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['Arrived_VAR_PERC']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),



     md_cnt_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#212070", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     md_cnt_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#212070", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     md_cnt_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#212070", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalmd_cnt_MONDAY = 0
        let totalmd_cnt_TUESDAY = 0
        let totalmd_cnt_WEDNESDAY = 0
        let totalmd_cnt_THURSDAY = 0
        let totalmd_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalmd_cnt_MONDAY += row['md_cnt_MONDAY']
          totalmd_cnt_TUESDAY += row['md_cnt_TUESDAY']
          totalmd_cnt_WEDNESDAY += row['md_cnt_WEDNESDAY']
          totalmd_cnt_THURSDAY += row['md_cnt_THURSDAY']
          totalmd_cnt_FRIDAY += row['md_cnt_FRIDAY']
        })
        return (totalmd_cnt_FRIDAY - ((totalmd_cnt_MONDAY + totalmd_cnt_TUESDAY + totalmd_cnt_WEDNESDAY + totalmd_cnt_THURSDAY)/4)) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['md_cnt_VAR']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),

     md_cnt_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#212070", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
       let totalmd_cnt_MONDAY = 0
        let totalmd_cnt_TUESDAY = 0
        let totalmd_cnt_WEDNESDAY = 0
        let totalmd_cnt_THURSDAY = 0
        let totalmd_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalmd_cnt_MONDAY += row['md_cnt_MONDAY']
          totalmd_cnt_TUESDAY += row['md_cnt_TUESDAY']
          totalmd_cnt_WEDNESDAY += row['md_cnt_WEDNESDAY']
          totalmd_cnt_THURSDAY += row['md_cnt_THURSDAY']
          totalmd_cnt_FRIDAY += row['md_cnt_FRIDAY']
        })
        return (totalmd_cnt_FRIDAY - ((totalmd_cnt_MONDAY + totalmd_cnt_TUESDAY + totalmd_cnt_WEDNESDAY + totalmd_cnt_THURSDAY)/4)) /
        ((totalmd_cnt_MONDAY + totalmd_cnt_TUESDAY + totalmd_cnt_WEDNESDAY + totalmd_cnt_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['md_cnt_VAR_PERC']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),



     session_cnt_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#d80b8c", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     session_cnt_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#d80b8c", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     session_cnt_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#d80b8c", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalsession_cnt_MONDAY = 0
        let totalsession_cnt_TUESDAY = 0
        let totalsession_cnt_WEDNESDAY = 0
        let totalsession_cnt_THURSDAY = 0
        let totalsession_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalsession_cnt_MONDAY += row['session_cnt_MONDAY']
          totalsession_cnt_TUESDAY += row['session_cnt_TUESDAY']
          totalsession_cnt_WEDNESDAY += row['session_cnt_WEDNESDAY']
          totalsession_cnt_THURSDAY += row['session_cnt_THURSDAY']
          totalsession_cnt_FRIDAY += row['session_cnt_FRIDAY']
        })
        return (totalsession_cnt_FRIDAY - ((totalsession_cnt_MONDAY + totalsession_cnt_TUESDAY + totalsession_cnt_WEDNESDAY + totalsession_cnt_THURSDAY)/4)) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['session_cnt_VAR']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),

     session_cnt_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#d80b8c", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalsession_cnt_MONDAY = 0
        let totalsession_cnt_TUESDAY = 0
        let totalsession_cnt_WEDNESDAY = 0
        let totalsession_cnt_THURSDAY = 0
        let totalsession_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalsession_cnt_MONDAY += row['session_cnt_MONDAY']
          totalsession_cnt_TUESDAY += row['session_cnt_TUESDAY']
          totalsession_cnt_WEDNESDAY += row['session_cnt_WEDNESDAY']
          totalsession_cnt_THURSDAY += row['session_cnt_THURSDAY']
          totalsession_cnt_FRIDAY += row['session_cnt_FRIDAY']
        })
        return (totalsession_cnt_FRIDAY - ((totalsession_cnt_MONDAY + totalsession_cnt_TUESDAY + totalsession_cnt_WEDNESDAY + totalsession_cnt_THURSDAY)/4)) /
        ((totalsession_cnt_MONDAY + totalsession_cnt_TUESDAY + totalsession_cnt_WEDNESDAY + totalsession_cnt_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['session_cnt_VAR_PERC']
        if (value > 0) {
          var color = '#008000'
        } else {
          var color = ' #e00000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),


     unfilled_cnt_AVG = colDef(
      name = "Mon-Thu Avg",
      maxWidth = 80,
      headerStyle = list(background = "#00aeef", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     unfilled_cnt_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#00aeef", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = 'sum',
      format = colFormat(separators = TRUE, digits = 0)),

     unfilled_cnt_VAR = colDef(
      name = "Var",
      maxWidth = 80,
      headerStyle = list(background = "#00aeef", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalunfilled_cnt_MONDAY = 0
        let totalunfilled_cnt_TUESDAY = 0
        let totalunfilled_cnt_WEDNESDAY = 0
        let totalunfilled_cnt_THURSDAY = 0
        let totalunfilled_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalunfilled_cnt_MONDAY += row['unfilled_cnt_MONDAY']
          totalunfilled_cnt_TUESDAY += row['unfilled_cnt_TUESDAY']
          totalunfilled_cnt_WEDNESDAY += row['unfilled_cnt_WEDNESDAY']
          totalunfilled_cnt_THURSDAY += row['unfilled_cnt_THURSDAY']
          totalunfilled_cnt_FRIDAY += row['unfilled_cnt_FRIDAY']
        })
        return (totalunfilled_cnt_FRIDAY - ((totalunfilled_cnt_MONDAY + totalunfilled_cnt_TUESDAY + totalunfilled_cnt_WEDNESDAY + totalunfilled_cnt_THURSDAY)/4)) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['unfilled_cnt_VAR']
        if (value > 0) {
          var color = '#e00000'
        } else {
          var color = '#008000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(separators = TRUE, digits = 0)),

     unfilled_cnt_VAR_PERC = colDef(
      name = "% Var",
      maxWidth = 80,
      headerStyle = list(background = "#00aeef", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalunfilled_cnt_MONDAY = 0
        let totalunfilled_cnt_TUESDAY = 0
        let totalunfilled_cnt_WEDNESDAY = 0
        let totalunfilled_cnt_THURSDAY = 0
        let totalunfilled_cnt_FRIDAY = 0
        rows.forEach(function(row) {
          totalunfilled_cnt_MONDAY += row['unfilled_cnt_MONDAY']
          totalunfilled_cnt_TUESDAY += row['unfilled_cnt_TUESDAY']
          totalunfilled_cnt_WEDNESDAY += row['unfilled_cnt_WEDNESDAY']
          totalunfilled_cnt_THURSDAY += row['unfilled_cnt_THURSDAY']
          totalunfilled_cnt_FRIDAY += row['unfilled_cnt_FRIDAY']
        })
        return (totalunfilled_cnt_FRIDAY - ((totalunfilled_cnt_MONDAY + totalunfilled_cnt_TUESDAY + totalunfilled_cnt_WEDNESDAY + totalunfilled_cnt_THURSDAY)/4)) /
        ((totalunfilled_cnt_MONDAY + totalunfilled_cnt_TUESDAY + totalunfilled_cnt_WEDNESDAY + totalunfilled_cnt_THURSDAY)/4) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['unfilled_cnt_VAR_PERC']
        if (value > 0) {
          var color = '#e00000'
        } else {
          var color = '#008000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),



No_Show_Rate_AVG = colDef(
 name = "Mon-Thu Avg",
 maxWidth = 80,
 headerStyle = list(background = "#a5a7a5", color = "white", fontWeight = "Bold", fontSize = "14px"),
 aggregate = JS("function(values, rows) {
   let totalNo_Show_MONDAY = 0
   let totalNo_Show_TUESDAY = 0
   let totalNo_Show_WEDNESDAY = 0
   let totalNo_Show_THURSDAY = 0
   let totalCanceled_MONDAY = 0
   let totalCanceled_TUESDAY = 0
   let totalCanceled_WEDNESDAY = 0
   let totalCanceled_THURSDAY = 0
   let totalRescheduled_MONDAY = 0
   let totalRescheduled_TUESDAY = 0
   let totalRescheduled_WEDNESDAY = 0
   let totalRescheduled_THURSDAY = 0
   let totalArrived_MONDAY = 0
   let totalArrived_TUESDAY = 0
   let totalArrived_WEDNESDAY = 0
   let totalArrived_THURSDAY = 0
   rows.forEach(function(row) {
     totalNo_Show_MONDAY += row['No_Show_MONDAY']
     totalNo_Show_TUESDAY += row['No_Show_TUESDAY']
     totalNo_Show_WEDNESDAY += row['No_Show_WEDNESDAY']
     totalNo_Show_THURSDAY += row['No_Show_THURSDAY']
     totalCanceled_MONDAY += row['Canceled_MONDAY']
     totalCanceled_TUESDAY += row['Canceled_TUESDAY']
     totalCanceled_WEDNESDAY += row['Canceled_WEDNESDAY']
     totalCanceled_THURSDAY += row['Canceled_THURSDAY']
     totalRescheduled_MONDAY += row['Rescheduled_MONDAY']
     totalRescheduled_TUESDAY += row['Rescheduled_TUESDAY']
     totalRescheduled_WEDNESDAY += row['Rescheduled_WEDNESDAY']
     totalRescheduled_THURSDAY += row['Rescheduled_THURSDAY']
     totalArrived_MONDAY += row['Arrived_MONDAY']
     totalArrived_TUESDAY += row['Arrived_TUESDAY']
     totalArrived_WEDNESDAY += row['Arrived_WEDNESDAY']
     totalArrived_THURSDAY += row['Arrived_THURSDAY']
   })
   return (totalNo_Show_MONDAY + totalNo_Show_TUESDAY + totalNo_Show_WEDNESDAY + totalNo_Show_THURSDAY +
           totalCanceled_MONDAY + totalCanceled_TUESDAY + totalCanceled_WEDNESDAY + totalCanceled_THURSDAY +
           totalRescheduled_MONDAY + totalRescheduled_TUESDAY + totalRescheduled_WEDNESDAY + totalRescheduled_THURSDAY) /
           (totalNo_Show_MONDAY + totalNo_Show_TUESDAY + totalNo_Show_WEDNESDAY + totalNo_Show_THURSDAY +
           totalCanceled_MONDAY + totalCanceled_TUESDAY + totalCanceled_WEDNESDAY + totalCanceled_THURSDAY +
           totalRescheduled_MONDAY + totalRescheduled_TUESDAY + totalRescheduled_WEDNESDAY + totalRescheduled_THURSDAY +
           totalArrived_MONDAY + totalArrived_TUESDAY + totalArrived_WEDNESDAY + totalArrived_THURSDAY) || '-'

 }"),
 style = JS("function(rowInfo) {
   var value = rowInfo.row['No_Show_Rate_AVG']
   if (value > 0) {
     var color = '#e00000'
   } else {
     var color = '#008000'
   }
   return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
 }"),
 format = colFormat(percent = TRUE, digits = 1)),


     No_Show_Rate_FRIDAY = colDef(
      name = "Fri",
      maxWidth = 80,
      headerStyle = list(background = "#a5a7a5", color = "white", fontWeight = "Bold", fontSize = "14px"),
      aggregate = JS("function(values, rows) {
        let totalNo_Show_FRIDAY = 0
        let totalCanceled_FRIDAY = 0
        let totalRescheduled_FRIDAY = 0
        let totalArrived_FRIDAY = 0
        rows.forEach(function(row) {
          totalNo_Show_FRIDAY += row['No_Show_FRIDAY']
          totalCanceled_FRIDAY += row['Canceled_FRIDAY']
          totalRescheduled_FRIDAY += row['Rescheduled_FRIDAY']
          totalArrived_FRIDAY += row['Arrived_FRIDAY']
        })
        return (totalNo_Show_FRIDAY + totalCanceled_FRIDAY + totalRescheduled_FRIDAY) /
        (totalNo_Show_FRIDAY + totalCanceled_FRIDAY + totalRescheduled_FRIDAY + totalArrived_FRIDAY) || '-'
      }"),
      style = JS("function(rowInfo) {
        var value = rowInfo.row['No_Show_Rate_FRIDAY']
        if (value > 0) {
          var color = '#e00000'
        } else {
          var color = ' #008000'
        }
        return { color: color, fontFamily: 'calibri', fontWeight: 'bold'}
      }"),
      format = colFormat(percent = TRUE, digits = 1)),

     appt_year = colDef(show =F),
     holiday = colDef(show =F),
     DEPARTMENT_ID = colDef(show =F),
     PROV_ID = colDef(show =F),
     NPI = colDef(show =F),
     Scheduled_MONDAY = colDef(show =F),
     Scheduled_TUESDAY = colDef(show =F),
     Scheduled_WEDNESDAY = colDef(show =F),
     Scheduled_THURSDAY = colDef(show =F),
     Scheduled_SATURDAY = colDef(show =F),
     Scheduled_SUNDAY = colDef(show =F),
     Arrived_MONDAY = colDef(show =F),
     Arrived_TUESDAY = colDef(show =F),
     Arrived_WEDNESDAY = colDef(show =F),
     Arrived_THURSDAY = colDef(show =F),
     Arrived_SATURDAY = colDef(show =F),
     Arrived_SUNDAY = colDef(show =F),
     md_cnt_MONDAY = colDef(show =F),
     md_cnt_TUESDAY = colDef(show =F),
     md_cnt_WEDNESDAY = colDef(show =F),
     md_cnt_THURSDAY = colDef(show =F),
     md_cnt_SATURDAY = colDef(show =F),
     md_cnt_SUNDAY = colDef(show =F),
     session_cnt_MONDAY = colDef(show =F),
     session_cnt_TUESDAY = colDef(show =F),
     session_cnt_WEDNESDAY = colDef(show =F),
     session_cnt_THURSDAY = colDef(show =F),
     session_cnt_SATURDAY = colDef(show =F),
     session_cnt_SUNDAY = colDef(show =F),
     unfilled_cnt_MONDAY = colDef(show =F),
     unfilled_cnt_TUESDAY = colDef(show =F),
     unfilled_cnt_WEDNESDAY = colDef(show =F),
     unfilled_cnt_THURSDAY = colDef(show =F),
     unfilled_cnt_SATURDAY = colDef(show =F),
     unfilled_cnt_SUNDAY = colDef(show =F),
     Canceled_MONDAY = colDef(show =F),
     Canceled_TUESDAY = colDef(show =F),
     Canceled_WEDNESDAY = colDef(show =F),
     Canceled_THURSDAY = colDef(show =F),
     Canceled_FRIDAY = colDef(show =F),
     Canceled_SATURDAY = colDef(show =F),
     Canceled_SUNDAY = colDef(show =F),
     Canceled_AVG = colDef(show =F),
     Rescheduled_MONDAY = colDef(show =F),
     Rescheduled_TUESDAY = colDef(show =F),
     Rescheduled_WEDNESDAY = colDef(show =F),
     Rescheduled_THURSDAY = colDef(show =F),
     Rescheduled_FRIDAY = colDef(show =F),
     Rescheduled_SATURDAY = colDef(show =F),
     Rescheduled_SUNDAY = colDef(show =F),
     Rescheduled_AVG = colDef(show =F),
     No_Show_MONDAY = colDef(show =F),
     No_Show_TUESDAY = colDef(show =F),
     No_Show_WEDNESDAY = colDef(show =F),
     No_Show_THURSDAY = colDef(show =F),
     No_Show_FRIDAY = colDef(show =F),
     No_Show_SATURDAY = colDef(show =F),
     No_Show_SUNDAY = colDef(show =F),
     No_Show_AVG = colDef(show =F)

  ) # Close Columns

  ) # Close Reactable
) # Close Taglist
) # Close htmltools


```

